% LaTeX resume using res.cls
\documentclass[line,margin]{res}

\begin{document}

\name{Travis M. Whitaker}
% \address used twice to have two lines of address
\address{262 Academy Street, Mexico, NY 13114}
\address{(315) 391-7268 \texttt{|} pi.boy.travis@gmail.com}
%\address{https://github.com/TravisWhitaker}

\begin{resume}

\section{EDUCATION} {\sl Bachelor of Science,} Chemical Engineering\\
Minor: Computer Engineering, Japanese Language \\
Rochester Institute of Technology, Rochester, NY, May 2016 \\

\section{EXPERIENCE} {\sl Process Data Modeling Engineer} \hfill June 2013 - Present \\
		Janssen Pharmaceuticals Research and Development,
		Philadelphia, PA
		\begin{itemize}  \itemsep -2pt
		\item   Worked with team developing high-performance numerical data modeling and analysis software, principally leveraging novel database technologies.
		\item   Maintain numerous large C and Haskell codebases.
		\item   Design domain-specific languages for modeling industrial processes, principally \\leveraging S88/S95 Recipe Framework.
		\item   Numerics optimization (GPU Programming, LLVM)
		\item   Distributed computing (Data Parallel Haskell, MPI, Ceph)
		\item   Implement graph database for process flow tracking and fault detection.
		\item   Extensive use of Amazon Web Services Cloud Computing Platform.
		\end{itemize}

                {\sl Research Assistant} \hfill Summer 2012 \\
                Applied Electrostatics Laboratory,
                SUNY Oswego, Oswego, NY
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                \item   Conducted experiments investigating applications of electrospray ionization.
		\item   Wrote software application in C
			for tracking individual particles
			to aid the analysis of high-speed footage
			of clouds of electrostatic particles
			produced via electrospray ionization.
                \end{itemize}

\section{SKILLS} {\sl Languages:} C, C++, Haskell, Python, R, Mathematica, MATLAB, \LaTeX, SQL, VHDL \\ \\
                 {\sl Coursework:} Continuum Mechanics, Reactor Engineering, Materials Science, Analytical Techniques \\ \\
                 Working knowledge of German and Japanese.

\section{PROFESSIONAL \\ INTERESTS, \\ HOBBIES, AND \\ PROJECTS}
				\begin{itemize} \itemsep -2pt
				\item	\emph{Resonator} -- Library of Parallel Implementations of Common Engineering Numerics Routines, principally PDEs and Tensor-Valued Systems.
				\item	\emph{Octothorpe} -- Cache-optimized thread-safe C data structures library.
				\item	\emph{libPOLY} -- Portable real-time sound synthesis library.
				\item	\emph{FermiShell} -- Small shell utility for solving chemical equations.
				\item	Digital Signal Processing
				\item	Computer Algebra
				\item	Embedded Systems Programming
				\item	High-Fidelity Audio
				\item	Discrete Electronics
				\end{itemize}

\section{PROFESSIONAL ORGANIZATIONS}
American Institute of Chemical Engineering\\
American Mathematical Society\\
American Chemical Society\\
Association of Computing Machinery\\
Computer Science House -- Reasearch \& Development Director 2014-2015\\

\end{resume}
\end{document}
